---
title: "Ion Concentrations in Puerto Rican Streams"
format: html
---

## Background

This project looks at concentrations of Ammonium, Calcium, Magnesium, Potassium and Ammonia in the years before and after a hurricane at four different sites in Puerto Rican Streams. The analysis uses a 9 week moving average to look at the levels of these nutrients from 1988 to 1994.

## Data

CSV files from [McDowell, William H., and USDA Forest Service. International Institute Of Tropical Forestry (IITF). 2024.](https://doi.org/10.6073/PASTA/F31349BEBDC304F758718F4798D25458).  Downloaded and stored within the repository.
```{r}
#| echo: false
#| output: false
#| warning: false

library(tidyverse)
clean_data <- read_csv("../output/output.csv")

# Put the nutrients in the correct order
clean_data$Nutrient <- factor(
  clean_data$Nutrient,
  levels = c("K", "NO3-N", "Mg", "Ca", "NH4-N")
)
```

## Methods

Create a "moving average" function to find a nine week moving average for the stream chemistry data.
Clean the data files by selecting relevant columns and adding a "sample ID" column to keep track of site location once files are combined.
Call the "moving_average" function on each dataframe.
Combine the moving_average output files into one larger data frame,  and pivot longer to create "nutrient" and "concentration" columns.
Put the nutrients in the correct order.


## Results

The results of this study show that the ion concentrations increased overall for most nutrients in the streams studied. Some streams and nutrients appeared to go back to normal after enough time has passed, while others stayed elevated.
```{r}
#| warning: false
ggplot(
  data = clean_data,
  mapping = aes(x = window_start, y = Concentration, linetype = Site)
) +
  geom_line() +
  facet_wrap(
    vars(Nutrient),
    scales = 'free_y',
    ncol = 1,
    strip.position = "left"
  ) +
  theme_bw() +
  labs(
    x = "Years",
    y = "Concentration",
    title = "Ion Concentrations in PR Streams"
  ) +
  geom_vline(
    xintercept = ymd("1989-09-17"),
    linetype = "dashed",
    color = "darkgrey"
  )
```